Ecostructure Global Geographic Motifs, v2

### 2019-10-04 reports/ecostructure_geo/ecostructure_geo.Rmd
Output combined figures for ecostructure geo report

```{r read-results, warning = FALSE, message = FALSE}
results_vector <- glue::glue(here("results/ecosfit_motif=geo_dataset=pteridos-no-obs_K={2:10}_tol=0.1_trials=1.RDS"))

@@

head(results_list[[1]][["theta"]])
head(results_list[[1]][["omega"]])
```

@@

# Loadd all_cells to get max and min lat/longs
loadd(all_cells, cache = ja_fern_cache)

# Read in high-resolution map of Japan, convert to sf
japan <- rnaturalearth::ne_countries(country = 'japan', scale = 'large') %>% sf::st_as_sf()

@@

# Convert data to long format, nested. Set K = 6
k_select = 6
geo_theta_nested <- results_list[[k_select - 1]][["theta"]] %>%
  as.data.frame %>%
  rownames_to_column("long_lat") %>%
  as_tibble %>%
  separate(long_lat, c("long", "lat"), sep = "_") %>%
  gather(motif, theta, -long, -lat) %>%
  mutate_at(vars(long, lat), as.numeric) %>%
# Check that longitude is between -180 and 180,
# that latitude is between -90 and 90, and that
# each long-lat-motif combination is unique
  verify(long > -180 & long < 180 & lat > -90 & lat < 90) %>%
  assert(is_uniq(c(.$long, .$lat, .$motif))) %>%
  group_by(motif) %>%
  nest

# Map over each theta plot separately so they each get their own
# scale.
geo_theta_plot_list <- map2(geo_theta_nested$data, geo_theta_nested$motif, make_geo_theta_plot)

@@

>>>>

```{r read-results, warning = FALSE, message = FALSE}
# Load ecostructure results
results_vector <- glue::glue(here("results/ecosfit_motif=geo_dataset=pteridos-no-obs_K={2:10}_tol=0.1_trials=1.RDS"))

@@

head(results_list[[1]][["theta"]])
head(results_list[[1]][["omega"]])

# Load all_cells to get max and min lat/longs
loadd(all_cells, cache = ja_fern_cache)

# Read in high-resolution map of Japan, convert to sf
japan <- rnaturalearth::ne_countries(country = 'japan', scale = 'large') %>% sf::st_as_sf()
```

@@

@@

make_geo_theta_plot_ja <- function (geo_theta_long, motif, occ_data) {
  ggplot(ggplot2::map_data("world"), aes(x = long, y = lat)) +
  geom_polygon(aes(group = group), fill = "light grey") +
  geom_raster(data = geo_theta_long, aes(fill = theta)) +
  scale_fill_gradient(low = "darkseagreen3", high = "red") +
  coord_quickmap(
      xlim = c(pull(occ_data, longitude) %>% min %>% floor, 
               pull(occ_data, longitude) %>% max %>% ceiling),
      ylim = c(pull(occ_data, latitude) %>% min %>% floor, 
               pull(occ_data, latitude) %>% max %>% ceiling)
    ) +
  labs(subtitle = motif) +
  jntools::blank_x_theme() +
  jntools::blank_y_theme() +
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(fill = "transparent"),
    panel.background = element_rect(fill = "transparent")
  )
}

# Convert data to long format, nested. Set K = 6
k_select = 6

# Global
geo_theta_nested <- results_list[[k_select - 1]][["theta"]] %>%
  as.data.frame %>%
  rownames_to_column("long_lat") %>%
  as_tibble %>%
  separate(long_lat, c("long", "lat"), sep = "_") %>%
  gather(motif, theta, -long, -lat) %>%
  mutate_at(vars(long, lat), as.numeric) %>%
# Check that longitude is between -180 and 180,
# that latitude is between -90 and 90, and that
# each long-lat-motif combination is unique
  verify(long > -180 & long < 180 & lat > -90 & lat < 90) %>%
  assert(is_uniq(c(.$long, .$lat, .$motif))) %>%
  group_by(motif) %>%
  nest

# Map over each theta plot separately so they each get their own
# scale.
# - Global plots
geo_theta_plot_list <- map2(geo_theta_nested$data, geo_theta_nested$motif, make_geo_theta_plot)

# - Japan-focused plots
geo_theta_plot_list_js <- 
  list(
    geo_theta_long = geo_theta_nested$data,
    motif = geo_theta_nested$motif,
    occ_data = list(all_cells)
  ) %>%
  pmap(make_geo_theta_plot_ja)

@@

## Combined plots

```{r combined-plot}
make_geo_theta_plot_color <- function (geo_theta_long, border_color) {
  ggplot(ggplot2::map_data("world"), aes(x = long, y = lat)) +
  geom_polygon(aes(group = group), fill = "light grey") +
  geom_raster(data = geo_theta_long, aes(fill = theta)) +
  scale_fill_gradient(low = "darkseagreen3", high = "red") +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  jntools::blank_x_theme() +
  jntools::blank_y_theme() +
  theme_void() +
  theme(
    legend.position = "none",
    plot.background = element_rect(fill = "transparent"),
    panel.background = element_rect(fill = "transparent"),
    panel.border = element_rect(colour = border_color, fill=NA, size=2)
  )
}

k_select <- 4

cols <- RColorBrewer::brewer.pal(k_select, name = "Set1")

ecos_plot_pie2(
    omega = results_list[[k_select - 1]][["omega"]],
    image_width = 6000*tweak,
    image_height = 4800*tweak,
    radius = 0.05,
    color = cols,
    bgmap_path = japan,
    long_lim = c(pull(all_cells, longitude) %>% min %>% floor, 
                 pull(all_cells, longitude) %>% max %>% ceiling),
    lat_lim =  c(pull(all_cells, latitude) %>% min %>% floor, 
                 pull(all_cells, latitude) %>% max %>% ceiling),
    path = glue::glue(here("reports/ecostructure_geo/geo_omega_combined_k={k_select}.png"))
  )

geo_theta_nested <- results_list[[k_select - 1]][["theta"]] %>%
  as.data.frame %>%
  rownames_to_column("long_lat") %>%
  as_tibble %>%
  separate(long_lat, c("long", "lat"), sep = "_") %>%
  gather(motif, theta, -long, -lat) %>%
  mutate_at(vars(long, lat), as.numeric) %>%
# Check that longitude is between -180 and 180,
# that latitude is between -90 and 90, and that
# each long-lat-motif combination is unique
  verify(long > -180 & long < 180 & lat > -90 & lat < 90) %>%
  assert(is_uniq(c(.$long, .$lat, .$motif))) %>%
  group_by(motif) %>%
  nest

geo_theta_plot_list_colors <- 
  list(
    geo_theta_long = geo_theta_nested$data,
    border_color = cols
  ) %>%
  pmap(make_geo_theta_plot_color)

# Combine into final plot and save
geo_theta_plot_colors <- patchwork::wrap_plots(geo_theta_plot_list_colors, ncol = 1)

ggsave(plot = geo_theta_plot_colors, filename = here(glue::glue("reports/ecostructure_geo/geo_theta_colors_k={k_select}.png")), width = 7, height = 8, units = "in")
